---
title: "231005In_Class_Exercise"
author: "Athena Zhang"
date: "2023-10-05"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# In-Class Exercise

```{r}
library(tidyverse)
```

```{r}
d <- read_csv("_DataPublic_/vdem/1984_2022/vdem_1984_2022_external.csv")
```

## 1. Codebook lookup

### 1.1 What indicators regarding the quality of education are available in the V-Dem datasets?

"e_peaveduc" = average years of education among citizens older than 15 "e_peedgini" = How unequal is the level of education achieved by the population aged 15 years and older?

### 1.2 What are the data's coverage (i.e., for which countries and years do we have data?)

1.2.1 Selecting:

```{r}
d_edu <- d |> 
  select(country_name, year, e_peaveduc, e_peedgini)
```

1.2.2 Renaming:

```{r}
d_edu <- d_edu |>
  rename("Country" = "country_name", "Year"="year", "Avg_Edu_Yrs"="e_peaveduc", "Edu_Gini"="e_peedgini")
```

```{r}
d_edu
```

1.2.3 Finding how many countries:

```{r}
d_edu |>
  distinct(Country) |>
  count()
```

**We have 181 countries**. Below are the individual countries.

```{r}
d_edu |> select(Country) |> distinct()
```

1.2.4 **We have data from 1984 to 2022** but some countries have missing data in some years. See below.

```{r}
d_edu|>
  mutate(Avg_edu_yrs_missing = as.numeric(is.na(Avg_Edu_Yrs)), .after = Avg_Edu_Yrs)|>
  group_by(Country)|>
  summarise(N_Year_missing = sum(Avg_edu_yrs_missing))

```

### 1.3 What are their sources? Provide the link to at least 1 source

<https://clio-infra.eu/Indicators/AverageYearsofEducation.html>

\^ Average years of Education (from Clio Infra)

<https://clio-infra.eu/Indicators/EducationalInequalityGiniCoefficient.html>

\^ Gini Coefficient for Educational Inequality (from Clio Infra)

## 2. Subset by columns

### 2.1 Create a dataset containing only the country-year identifiers and indicators of education quality

See section 1.2.1

### 2.2 Rename the columns of education quality to make them informative

See section 1.2.2

"Avg_Edu_Yrs"="e_peaveduc"

"Edu_Gini"="e_peedgini"

## 3. Subset by rows

### 3.1 List 5 countries-years that have the highest education level among its population

```{r}
d_edu |>
  slice_max(order_by = Avg_Edu_Yrs, n = 5, with_ties = FALSE)
```

### 3.2 List 5 countries-years that suffer from the most severe inequality in education.

```{r}
d_edu |>
  slice_max(order_by = Edu_Gini, n = 5)
```

## 4. Summarise the data

### 4.1 Check data availability: For which countries and years are the indicators of education quality available?

See section 1.2.4

### 4.2 Create two types of country-level indicators of education quality

1.  Average level of education quality from 1984 to 2022

```{r}
d_edu |>
  group_by(Country) |>
  summarise(Avg_Edu_Level = mean(Avg_Edu_Yrs, na.rm = TRUE), Avg_Gini = mean(Edu_Gini, na.rm = TRUE)) |>
  arrange(Avg_Edu_Level)
```

2.  Change of education quality from 1984 to 2022

```{r}
d_edu |>
  group_by(Country)|>
  arrange(Year)|>
  summarise(Edu_quality_2022_1984 = (last(Avg_Edu_Yrs)-first(Avg_Edu_Yrs)) / first(Avg_Edu_Yrs))|>
  ungroup() |>
  arrange(Edu_quality_2022_1984)
```

### 4.3 Examine the data and briefly discuss: Which countries perform the best and the worst in terms of education quality in the past four decades?

On average, Burkina Faso, Niger, Mali, Somalia, and Burundi, from lowest to highest respectively, have the lowest avaerage years of education among citizens above 15.

However, countries like Sweden, Belarus, Australia, Moldova, and Namibia have experienced the least change in average education years over the past four decades.

On the other hand, Germany, Australia, United Kingdom, Canada, and Switzerland have the highest average education years among citizens above 15.
