---
title: "Notes_Data_Wrangling_2"
author: "Athena Zhang"
date: "2023-10-05"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Wrangling Cont.

## 0. Import data

```{r}
d <- read_csv("_DataPublic_/vdem/1984_2022/vdem_1984_2022_external.csv")
```

## 1. Reshape the V-Dem dataset

*e.g. want: each row contain country-year-variable (new dataset is a country-year-observation)*

```{r}
d |> select(country_name) |> distinct()

```

```{r}
d_subset <- d |> select(country_name, year, starts_with("e_"))
View(d_subset)
```

```{r}
d_subset_long <-
  d_subset |> pivot_longer(cols = starts_with("e_"))
View(d_subset_long)
```

*e.g. want: widen the above long table so that each Year has its own column*

```{r}
d_subset_wide_year <-
  d_subset_long |> pivot_wider(names_from = year, values_from = value)
View(d_subset_wide_year)
```

## 2. Stack multiple subsets of the V-Dem datasets by row and by columns

*e.g. merge the datasets of the V-dem data **by columns***

```{r}
d_VdemIndex <- read.csv("_DataPublic_/vdem/1984_2022/vdem_1984_2022_index.csv")
```

```{r}
d_stack <- bind_cols(d, d_VdemIndex)
View(d_stack)
```

*e.g. merge two datasetes of the V-dem data **by rows***

```{r}
d_1945_1983 <- read.csv("_DataPublic_/vdem/1945_1983/vdem_1945_1983_external.csv")
View(d_1945_1983)
```

```{r}
d_1945_2022 <- bind_rows(d, d_1945_1983)
View(d_1945_2022)
```

```{r}
d_1945_2022 |> select(year) |> distinct() |> arrange(year)
```
